Manifold Destiny - or how to rig an election

### 2024-01-08 paper.qmd
addedpoly

:::: {.columns}
::: {.column width="50%"}
Case 1
:::
```{r, echo=F}
clr <- c("black","green","red","blue")
lego_hux_imp_i <- as_hux(towi[,1:3]) %>%
  set_text_color(5, 1:2, clr[1]) %>%
  set_background_color(1, 1:3, clr[2]) %>% 
  set_background_color(2, 1:3, clr[3]) %>%
  set_background_color(3, 1:3, clr[4]) %>%
  set_background_color(4, 2:3, clr[4]) %>%
  set_background_color(5, 3:3, clr[4]) %>%
  set_font_size(16)

lego_hux_imp_i
```

@@

**20 laws and 40 isometris**

```{r}
#kable(laws_df1, format = "markdown", escape = FALSE) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=12)
```

**20 laws and 40 isometris**

@@

kable(laws_df, format = "markdown", escape = FALSE)

@@

# Combine the columns
combined <- data.frame(
  V1 = matrix(c(rbind(V1, Equation1)), ncol = 1),
  V2 = matrix(c(rbind(V2, Equation2)), ncol = 1),
  V3 = matrix(c(rbind(V3, Equation3)), ncol = 1),
  V4 = matrix(c(rbind(V4, Equation4)), ncol = 1)
)
kable(combined, format = "markdown", escape = FALSE)
```

@@

::: {.column width="40%"}

Non-rigged election using standard form
```{r, echo=F, echo=F, out.width="150%", fig.cap=""}
#0app_n_out[[4]] 
```

@@

::: {.column width="60%"}

Rigged election using standard form
```{r, echo=F, echo=F, out.width="150%", fig.cap=""}
#app
```

@@

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=
`r #paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
\end{equation*}

Election outome
```{r, echo=F}
#sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
```

@@

$f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$

Election outome
```{r, echo=F}
#sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
```

@@

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=
`r #paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
\end{equation*}

@@

$f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$

>>>>

:::: {.columns}
::: {.column width="50%"}
Case 1
:::
```{r, echo=F}
clr <- c("black","green","red","blue")
lego_hux_imp_i <- as_hux(towi[,1:3]) %>%
  set_text_color(5, 1:2, clr[1]) %>%
  set_background_color(1, 1:3, clr[2]) %>% 
  set_background_color(2, 1:3, clr[3]) %>%
  set_background_color(3, 1:3, clr[4]) %>%
  set_background_color(4, 2:3, clr[4]) %>%
  set_background_color(5, 3:3, clr[4]) %>%
  set_font_size(16)
lego_hux_imp_i
```

@@

::: {.callout-caution collapse="true"}
**20 laws and 40 isometris**

@@

kable(laws_df, format = "markdown", escape = FALSE) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)

@@

# Combine the columns
combined <- data.frame(
  V1 = matrix(c(rbind(V1, Equation1)), ncol = 1),
  V2 = matrix(c(rbind(V2, Equation2)), ncol = 1),
  V3 = matrix(c(rbind(V3, Equation3)), ncol = 1),
  V4 = matrix(c(rbind(V4, Equation4)), ncol = 1)
)
kable(combined, format = "markdown", escape = FALSE) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```

@@

::: {.column width="50%"}
Non-rigged election using standard form
```{r}
app_n_out[[4]] 
```

@@

Rigged election using standard form
```{r}
app_ex1_out[[4]] 
```

@@

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
\end{equation*}

@@

$f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$

@@

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
\end{equation*}

@@

$f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
